---
title: "Build models for use"
author: "Sara Gosline"
date: "7/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../beatAMLdata.R")
library(amlresistancenetworks)
```

## Load data
We have created a standard file to load all the data needed for the analysis.

```{r load data,warning=FALSE}
loadBeatAMLData()
```

## Now we can build the models

We want to build both the LASSO and logistic regression models using the following code. This code will divide the patients into 5 batches and train/test the model holding out 1/5 of the data each time. Then we will have predictions on each of the samples. 

```{r build models, warning=FALSE}
all.pats <- intersect(pat.data$`AML sample`,auc.dat$`AML sample`)
library(caret)
folds<-createFolds(all.pats,k=5)
##separate out data?

res<-lapply(folds,function(testpats){
    test.pats<-all.pats[testpats]
    train.pats<-setdiff(all.pats,test.pats)

    print("Phospho preds first")
      substrate.dat<-pat.phos%>%
        dplyr::select(`AML sample`='Sample',Gene='site',Phosphosite='LogFoldChange')
  
      tr.dat<-subset(substrate.dat,`AML sample`%in%train.pats)
      te.dat<-subset(substrate.dat,`AML sample`%in%test.pats)
      
      phospho.reg.results<-drugMolRegressionEval(auc.dat,
                                                 tr.dat,
                                               'Phosphosite',
                                               dplyr::rename(auc.dat,Sample='AML sample'),
                                               dplyr::rename(te.dat,Sample='AML sample'))%>%
        do.call(rbind,.)
      
    
    phospho.lr.results<-drugMolLogRegEval(auc.dat,tr.dat,'Phosphosite',
                                          dplyr::rename(auc.dat,Sample='AML sample'),
                                           dplyr::rename(te.dat,Sample='AML sample'))%>%
      do.call(rbind,.)
  
    print('Now getting gene-based preds')

      tr.dat<-subset(pat.data,`AML sample`%in%train.pats)
      te.dat<-subset(pat.data,`AML sample`%in%test.pats)
    
    ##now train model on AML and eval on depmap data
  reg.preds<-purrr::map_df(list(mRNA='mRNALevels',
                              protein='proteinLevels',
                            #  gene='geneMutations',
                               binGene='binaryMutations'),
                         ~ drugMolRegressionEval(auc.dat,
                                                 tr.dat,
                                                 .x,
                                              dplyr::rename(auc.dat,Sample='AML sample'),
                                               dplyr::rename(te.dat,Sample='AML sample'),
                                                 category='Condition'))

    print("Comparing logistic preds")
  log.reg.preds<-purrr::map_df(list(protein='proteinLevels',
                                  mRNA='mRNALevels',
                           #   gene='geneMutations',
                              binGene='binaryMutations'),
                             ~ drugMolLogRegEval(auc.dat,
                                                 tr.dat,
                                                 .x,
                                              dplyr::rename(auc.dat,Sample='AML sample'),
                                               dplyr::rename(te.dat,Sample='AML sample'),
                                                 category='Condition'))


 


  lr.results<-rbind(log.reg.preds,phospho.lr.results)%>%
    mutate(method='LogisticReg')%>%
    mutate(MSE=MSE*10000)
  
  full.results<-rbind(reg.preds,phospho.reg.results)%>%
    mutate(method='LASSO')
  saveRDS(full.results,'lassoRegPreds.rds')
  saveRDS(lr.results,'logRegPreds.rds')

  full.results<-rbind(full.results,lr.results)
  return(full.results)
#  saveRDS(full.results,'mostlyCompletePredictions.rds')
})

all.res<-do.call(rbind,res)

saveRDS(all.res,'combinedLogLassok5fold.rds')

```
Now we have all the performance across all folds. Let's plot this instead of the original performance across all data types

```{r kfold performance plots}

```