---
title: "Build K-fold models for use"
author: "Sara Gosline"
date: "10/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../beatAMLdata.R")
library(amlresistancenetworks)
```

## Load data
We have created a standard file to load all the data needed for the analysis.

```{r load data,warning=FALSE, message=FALSE}
loadBeatAMLData()

pat.data<- pat.data%>%
  left_join(rename(pat.phos,`AML sample`='Sample',Phosphosite='LogFoldChange'))
```

## Now we can build the models

We want to build both the LASSO and logistic regression models using the following code. This code will divide the patients into 3 batches and train/test the model holding out 1/3 of the data each time. Then we will have predictions on each of the samples. 

```{r build models, warning=FALSE, message=FALSE}

all.pats <- intersect(pat.data$`AML sample`,auc.dat.fam$`AML sample`)
library(caret)
folds<-createFolds(all.pats,k=5)
##separate out data?

res<-lapply(folds,function(testpats){
    test.pats<-all.pats[testpats]
    train.pats<-setdiff(all.pats,test.pats)

    
  tr.dat<-subset(pat.data,`AML sample`%in%train.pats)
  te.dat<-subset(pat.data,`AML sample`%in%test.pats)
  
      ##This list describes the features to be used  
  eval.list<-list(
    combo=list(mf=c('Gene','Gene','Gene','site'),
               fn=c('mRNALevels','proteinLevels','binaryMutations','Phosphosite')),
    mRNA=c('Gene','mRNALevels'),
    prot=c("Gene","proteinLevels"),
    mut=c('Gene','binaryMutations'),
    phosph=c('site','Phosphosite'))

    message("Comparing logistic preds")
  log.reg.preds<-purrr::map_df(eval.list,
                             ~ drugMolLogRegEval(auc.dat,
                                                tr.dat,
                                               mol.feature=.x[1],
                                                            mol.feature.name=.x[2],
                                         dplyr::rename(auc.dat,Sample='AML sample'),
                                               dplyr::rename(te.dat,Sample='AML sample'),
                                              category='family'))

      
  message('Running lasso')
    ##now train model on AML and eval on depmap data
  reg.preds<-purrr::map_df(eval.list,
                         ~ amlresistancenetworks::drugMolRegressionEval(auc.dat,
                            tr.dat,
                            mol.feature=.x[1],
                            mol.feature.name=.x[2],                                                   
                            dplyr::rename(auc.dat,Sample='AML sample'),
                                             dplyr::rename(te.dat,Sample='AML sample'),
                                                 category='family'))
  message("Running elastic net")
  enet.reg.preds<-purrr::map_df(eval.list,
                         ~ drugMolRegressionEval(auc.dat,
                            tr.dat,
                             mol.feature=.x[1],
                                mol.feature.name=.x[2],
                                          dplyr::rename(auc.dat,Sample='AML sample'),
                                               dplyr::rename(te.dat,Sample='AML sample'),
                                                 category='family',doEnet=TRUE))
  
  
  

  e.results<-enet.reg.preds%>%
    mutate(method='ElasticNet')
 
  full.results<-reg.preds%>%
    mutate(method='LASSO')

  lr.results<-log.reg.preds%>%
    mutate(method='LogisticReg')%>%
    mutate(MSE=MSE*10000)
  
  #full.results<-rbind(full.results,lr.results)
  saveRDS(full.results,'lassoRegPreds.rds')
  saveRDS(lr.results,'logRegPreds.rds')
  saveRDS(e.results,'enetRegPreds.rds')
#  saveRDS(full.results,'mostlyCompletePredictions.rds')
  
  all.res<-rbind(full.results,lr.results,e.results)
  print(dim(all.res))
  return(all.res)
  
})

res<-do.call(rbind,res)
saveRDS(res,'combinedKfoldResFamily.rds')
```

Now we have all the data files and ready to go!

Let's plot the k-fold results by data type. 
```{r plot results}
library(ggplot2)

library(wesanderson)
pal<-wes_palette('Darjeeling1')

p3<-res%>%
  subset(numFeatures>0)%>%
    ggplot(aes(y=corVal,x=Molecular,fill=Molecular))+
          geom_boxplot(aes(alpha=0.5))+
          geom_jitter(aes(color=Molecular))+
  scale_color_manual(values=pal)+
scale_fill_manual(values=pal)+facet_grid(~method)

p3

ggsave('5foldCVFamilyperformance.pdf',p3,width=12)

```

It seems that the protein data performs well. We can break down by drug as well to see how individual drug families perform.

```{r plot drugs, message=F}

  p4<-res%>%subset(numFeatures>0)%>%
    ggplot(aes(y=corVal,x=compound,fill=Molecular))+
          geom_boxplot(aes(alpha=0.5))+
          geom_jitter(aes(color=Molecular))+
  scale_color_manual(values=pal)+
scale_fill_manual(values=pal)+coord_flip()+facet_grid(~method)

p4

ggsave('5foldCVperformanceByDrugFamily.pdf',p4,height=12,width=12)
```