---
title: "Build K-fold models for use"
author: "Sara Gosline"
date: "10/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../beatAMLdata.R")
library(amlresistancenetworks)
```

## Load data
We have created a standard file to load all the data needed for the analysis. We also merge the gene based data and the phosphosite data by Gene and Sample

```{r load data, error=FALSE, message=FALSE, warning=FALSE}
loadBeatAMLData()

pat.data<- pat.data%>%
  left_join(rename(pat.phos,`AML sample`='Sample',Phosphosite='LogFoldChange'))

##get file from synapse
syn<-amlresistancenetworks::synapseLogin()
res<-readRDS(syn$get('syn26529375')$path)
##load file
```


Now we have all the data files and ready to go!

Let's plot the k-fold results by data type. 
```{r plot results}
library(ggplot2)

library(wesanderson)
pal<-wes_palette('Darjeeling1')

p3<-res%>%
  subset(numFeatures>0)%>%
    ggplot(aes(y=corVal,x=Molecular,fill=Molecular))+
          geom_boxplot(aes(alpha=0.5))+
          geom_jitter(aes(color=Molecular))+
  scale_color_manual(values=pal)+
scale_fill_manual(values=pal)+facet_grid(~method)

p3
write.csv(res%>%group_by(Molecular,method)%>%summarize(meanCor=mean(corVal,na.rm=T))%>%
            arrange(desc(meanCor)),file='table1_overallPerf.csv')
ggsave('5foldCVperformance.pdf',p3,width=12)

```

It seems that the protein data performs well. We can break down by drug as well to see how individual drugs perform.

```{r plot drugs, message=F}

  p4<-res%>%subset(numFeatures>0)%>%
    ggplot(aes(y=corVal,x=compound,fill=Molecular))+
          geom_boxplot(aes(alpha=0.5))+
       #   geom_jitter(aes(color=Molecular))+
  scale_color_manual(values=pal)+
scale_fill_manual(values=pal)+coord_flip()+facet_grid(~method)

p4

write.csv(res%>%group_by(Molecular,method,compound)%>%summarize(meanCor=mean(corVal,na.rm=T),samples=mean(numSamples,na.rm=T))%>%arrange(desc(meanCor)),'table2.csv')
ggsave('5foldCVperformanceByDrug.pdf',p4,height=12,width=10)

```

Now we can  save the gene lists to synapse
```{r warning=FALSE, message=FALSE}

  pred.lists<-do.call(rbind,apply(res,1,function(x){
    res2<-getFeaturesFromStringdf(x[['genes']],x[['Molecular']])
   # print(as.data.frame(t(x)))
    res2%>%left_join(as.data.frame(t(x)),by='Molecular')
  }))%>%
     select(-genes)%>%
  #  left_join(eval.sum)%>%
    arrange(desc(corVal))

  write.csv(pred.lists,file='fiveFoldModelFeaturesAndPerf.csv')
# synTableStore(pred.lists,'Regression crossvalidation from all pilot data',parentId = 'syn22128879')

```