---
title: "Assess performance of family drug modeling using K-fold cross validation"
author: "Sara Gosline"
date: "10/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../beatAMLdata.R")
library(amlresistancenetworks)
```

## Load data and models
We have created a standard file to load all the data needed for the analysis. We want to build both the LASSO and logistic regression models using the following code. This code will divide the patients into 3 batches and train/test the model holding out 1/3 of the data each time. Then we will have predictions on each of the samples. 

```{r load data,warning=FALSE, message=FALSE}
loadBeatAMLData()

pat.data<- pat.data%>%
  left_join(rename(pat.phos,`AML sample`='Sample',Phosphosite='LogFoldChange'))
syn<-synapseLogin()
res<-readRDS(syn$get('syn26529371')$path)

```

Now we have all the data files and ready to go!

Let's plot the k-fold results by data type. 
```{r plot results}
library(ggplot2)

library(wesanderson)
pal<-wes_palette('Darjeeling1')

p3<-res%>%
  subset(numFeatures>0)%>%
    ggplot(aes(y=corVal,x=Molecular,fill=Molecular))+
          geom_boxplot(aes(alpha=0.5))+
          geom_jitter(aes(color=Molecular))+
  scale_color_manual(values=pal)+
scale_fill_manual(values=pal)+facet_grid(~method)

p3

ggsave('5foldCVFamilyperformance.pdf',p3,width=12)

```

It seems that the protein data performs well. We can break down by drug as well to see how individual drug families perform.

```{r plot drugs, message=F}

  p4<-res%>%subset(numFeatures>0)%>%
    ggplot(aes(y=corVal,x=compound,fill=Molecular))+
          geom_boxplot(aes(alpha=0.5))+
          geom_jitter(aes(color=Molecular))+
  scale_color_manual(values=pal)+
scale_fill_manual(values=pal)+coord_flip()+facet_grid(~method)

p4

ggsave('5foldCVperformanceByDrugFamily.pdf',p4,height=12,width=12)
```