---
title: "Build K-fold models for use"
author: "Sara Gosline"
date: "10/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../beatAMLdata.R")
library(amlresistancenetworks)
```

## Load data
We have created a standard file to load all the data needed for the analysis. We also merge the gene based data and the phosphosite data by Gene and Sample

```{r load data, error=FALSE, message=FALSE, warning=FALSE}
loadBeatAMLData()

##u
##create combined data frame of gene and phosphosite

pat.data<- pat.data%>%
  left_join(rename(pat.phos,`AML sample`='Sample',Phosphosite='LogFoldChange'))

```

## Now we can build the models

We want to build both the LASSO and logistic regression models using the following code. This code will divide the patients into 5 batches and train/test the model holding out 1/5 of the data each time. Then we will have predictions on each of the samples. 


```{r build models, warning=FALSE, message=FALSE, error=FALSE}

if(file.exists('combinedKfoldRes.rds')){
  
  res<-readRDS('combinedKfoldRes.rds')
  
}else{

all.pats <- intersect(pat.data$`AML sample`,auc.dat$`AML sample`)
library(caret)
folds<-createFolds(all.pats,k=5)
##separate out data?

  res<-lapply(folds,function(testpats){
      test.pats<-all.pats[testpats]
      train.pats<-setdiff(all.pats,test.pats)
  
    print('Now getting gene-based preds')
  
    tr.dat<-subset(pat.data,`AML sample`%in%train.pats)
    te.dat<-subset(pat.data,`AML sample`%in%test.pats)
  
    ##This list describes the features to be used  
    eval.list<-list(
      combo=list(mf=c('Gene','Gene','Gene','site'),
                 fn=c('mRNALevels','proteinLevels','binaryMutations','Phosphosite')),
      mRNA=c('Gene','mRNALevels'),
      prot=c("Gene","proteinLevels"),
      mut=c('Gene','binaryMutations'),
      phosph=c('site','Phosphosite'))
  
      message("Comparing logistic preds")
    log.reg.preds<-purrr::map_df(eval.list,
                               ~ drugMolLogRegEval(auc.dat,
                                                  tr.dat,
                                                 mol.feature=.x[1],
                                                              mol.feature.name=.x[2],
                                           dplyr::rename(auc.dat,Sample='AML sample'),
                                                 dplyr::rename(te.dat,Sample='AML sample'),
                                                category='Condition'))
    
          
    message('Running lasso')
      ##now train model on AML and eval on depmap data
    reg.preds<-purrr::map_df(eval.list,
                           ~ amlresistancenetworks::drugMolRegressionEval(auc.dat,
                              tr.dat,
                              mol.feature=.x[1],
                              mol.feature.name=.x[2],                                                   
                              dplyr::rename(auc.dat,Sample='AML sample'),
                                               dplyr::rename(te.dat,Sample='AML sample'),
                                                   category='Condition'))
    message("Running elastic net")
    enet.reg.preds<-purrr::map_df(eval.list,
                           ~ drugMolRegressionEval(auc.dat,
                              tr.dat,
                               mol.feature=.x[1],
                                  mol.feature.name=.x[2],
                                            dplyr::rename(auc.dat,Sample='AML sample'),
                                                 dplyr::rename(te.dat,Sample='AML sample'),
                                                   category='Condition',doEnet=TRUE))
    
    
    
  
    e.results<-enet.reg.preds%>%
      mutate(method='ElasticNet')
   
    full.results<-reg.preds%>%
      mutate(method='LASSO')
  
    lr.results<-log.reg.preds%>%
      mutate(method='LogisticReg')%>%
      mutate(MSE=MSE*10000)
  
  #full.results<-rbind(full.results,lr.results)
  #saveRDS(full.results,'lassoRegPreds.rds')
  #saveRDS(lr.results,'logRegPreds.rds')
  #saveRDS(e.results,'enetRegPreds.rds')
    all.res<-rbind(full.results,lr.results,e.results)
  print(dim(all.res))
  return(all.res)
  
  })

  res<-do.call(rbind,res)
  saveRDS(res,'combinedKfoldRes.rds')
}
```

Now we have all the data files and ready to go!

Let's plot the k-fold results by data type. 
```{r plot results}
library(ggplot2)

library(wesanderson)
pal<-wes_palette('Darjeeling1')

p3<-res%>%
  subset(numFeatures>0)%>%
    ggplot(aes(y=corVal,x=Molecular,fill=Molecular))+
          geom_boxplot(aes(alpha=0.5))+
          geom_jitter(aes(color=Molecular))+
  scale_color_manual(values=pal)+
scale_fill_manual(values=pal)+facet_grid(~method)

p3
write.csv(res%>%group_by(Molecular,method)%>%summarize(meanCor=mean(corVal,na.rm=T))%>%
            arrange(desc(meanCor)),file='table1_overallPerf.csv')
ggsave('5foldCVperformance.pdf',p3,width=12)

```

It seems that the protein data performs well. We can break down by drug as well to see how individual drugs perform.

```{r plot drugs, message=F}

  p4<-res%>%subset(numFeatures>0)%>%
    ggplot(aes(y=corVal,x=compound,fill=Molecular))+
          geom_boxplot(aes(alpha=0.5))+
       #   geom_jitter(aes(color=Molecular))+
  scale_color_manual(values=pal)+
scale_fill_manual(values=pal)+coord_flip()+facet_grid(~method)

p4

write.csv(res%>%group_by(Molecular,method,compound)%>%summarize(meanCor=mean(corVal,na.rm=T),samples=mean(numSamples,na.rm=T))%>%arrange(desc(meanCor)),'table2.csv')
ggsave('5foldCVperformanceByDrug.pdf',p4,height=12,width=10)

```

Now we can  save the gene lists to synapse
```{r warning=FALSE, message=FALSE}

  pred.lists<-do.call(rbind,apply(res,1,function(x){
    res2<-getFeaturesFromString(x[['genes']],x[['Molecular']])
   # print(as.data.frame(t(x)))
    res2%>%left_join(as.data.frame(t(x)),by='Molecular')
  }))%>%
     select(-genes)%>%
  #  left_join(eval.sum)%>%
    arrange(desc(corVal))

  write.csv(pred.lists,file='fiveFoldModelFeaturesAndPerf.csv')
# synTableStore(pred.lists,'Regression crossvalidation from all pilot data',parentId = 'syn22128879')

```