---
title: "Build models for use"
author: "Sara Gosline"
date: "7/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../beatAMLdata.R")
library(amlresistancenetworks)
```

## Load data
We have created a standard file to load all the data needed for the analysis.

```{r load data,warning=FALSE}
loadBeatAMLData()
```

## Now we can build the models

We want to build both the LASSO and logistic regression models using the following code. This code will divide the patients into 3 batches and train/test the model holding out 1/3 of the data each time. Then we will have predictions on each of the samples. 

```{r build models, warning=FALSE}

##separate out data?
test.pats
train.pats

 print("Phospho preds first")
  substrate.dat<-pat.phos%>%
    dplyr::select(`AML sample`='Sample',Gene='site',Phosphosite='LogFoldChange')
  
  phospho.reg.results<-drugMolRegressionEval(auc.dat,substrate.dat,'Phosphosite')
  phospho.lr.results<-drugMolLogRegEval(auc.dat,substrate.dat,'Phosphosite')
  
  print('Now getting gene-based preds')
  
    ##now train model on AML and eval on depmap data
  reg.preds<-purrr::map_df(list(mRNA='mRNALevels',
                              protein='proteinLevels',
                            #  gene='geneMutations',
                               binGene='binaryMutations'),
                         ~ drugMolRegressionEval(auc.dat,
                                                 pat.data,
                                                 .x,
                                                 ctrp.cl.auc,
                                                 cl.mol.dat,
                                                 category='Condition'))
    print("Comparing logistic preds")
  log.reg.preds<-purrr::map_df(list(protein='proteinLevels',
                                  mRNA='mRNALevels',
                           #   gene='geneMutations',
                              binGene='binaryMutations'),
                             ~ drugMolLogRegEval(auc.dat,
                                                pat.data,
                                                .x,
                                               ctrp.cl.auc,
                                               cl.mol.dat,
                                              category='Condition'))

  ##now train model on AML and eval on depmap data
  log.reg.preds<-purrr::map_df(list(mRNA='mRNALevels',
                              protein='proteinLevels',
                            #  gene='geneMutations',
                               binGene='binaryMutations'),
                         ~ drugMolRegressionEval(auc.dat,
                                                 pat.data,
                                                 .x,
                                                 ctrp.cl.auc,
                                                 cl.mol.dat,
                                                 category='Condition'))


 
  full.results<-rbind(reg.preds,phospho.reg.results)%>%
    mutate(method='LASSO')

  lr.results<-rbind(logr.preds,phospho.lr.results)%>%
    mutate(method='LogisticReg')%>%
    mutate(MSE=MSE*10000)
  
  #full.results<-rbind(full.results,lr.results)
  saveRDS(full.results,'lassoRegPreds.rds')
  saveRDS(lr.results,'logRegPreds.rds')
#  saveRDS(full.results,'mostlyCompletePredictions.rds')
  
 ```
Now we have all the data files and ready to go!