---
title: "Figure 4-5 Candidates signatures from LOO cross validation"
author: "Sara Gosline"
date: "02/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(amlresistancenetworks)
library(wesanderson)
library(DT)

source("../beatAMLdata.R")

pal<-wes_palette("Darjeeling1")
if(!exists('dataLoaded')){
  loadBeatAMLData()
  #loadUnNormPhosData()
  dataLoaded=TRUE
}


```

Now let's load the full models to assess signatures

```{r build sigs,warning=F,message=F}

 ##lets load up original preds too
  #eval.preds<-readRDS('combinedKfoldRes.rds')
  
##get file from synapse
syn<-amlresistancenetworks::synapseLogin()
eval.preds<-readRDS(syn$get('syn26529375')$path)
all.preds<-readRDS(syn$get('syn26529376')$path)all.preds<-readRDS(syn$get('syn26529376')$path)

tr.dat<- pat.data%>%
    left_join(rename(pat.phos,`AML sample`='Sample',Phosphosite='LogFoldChange'))
  
  
```

## Evaluate Functional role of the signatures


Given the diversity of signatures obtained from the predictive models, we use the signatures from the complete models and the performance from K-means validation to identify specific gene signatures. 

```{r lasso preds,warning=FALSE,echo=FALSE}


#'
#'selectDataMatAndPlot matches the output of a predictor (new.results) to the AUC data
#'and original molecular data to create heatmap
#'and combines ith with the specified data type and passes along a method to be used
#'@param drugName
#'@param meth
#'@param data
#'@return output of prediction
selectDataMatAndPlot<-function(drugName,method,data,genes,doEnrich=FALSE,doGraph=FALSE){
  #get dimensionality-reduced samples
  if(data%in%c('proteinLevels','mRNALevels','geneMutations','binaryMutations') &&!is.null(tr.dat)){
    data.mat<-tr.dat%>%
      dplyr::rename(value=data,Sample='AML sample')
  # }else if(data=='Phosphosite'&&!is.null(pat.phos)){
  #  data.mat<-pat.phos%>%
  #    dplyr::select(Gene='site',Sample,value='LogFoldChange')
  }else if(data=='Phosphosite'){
    ##build combined matrix...
      data.mat<-tr.dat%>%
        dplyr::select(-Gene)%>%
      dplyr::rename(value=data,Gene='site',Sample='AML sample')

    }else{
    print(paste("Do not have data for",data))
    return(NULL)
  }
  
  auc.d<-auc.dat%>%
    dplyr::select(-c(medAUC,percAUC,overallSurvival,ageAtDiagnosis,family))%>%
    dplyr::rename(Sample='AML sample')

  #genes=getFeaturesFromString(genelist,data)
  clusterSingleDrugEfficacy(drugName,method,data,doEnrich=doEnrich,
                              this.auc.dat=auc.d,auc.thresh=100,
                            genes,data.mat)%>%
    subset(p.adjust<0.05)  

  
  
  }

  eval.sum<-eval.preds%>%dplyr::select(compound,Molecular,method,corVal)%>%
    group_by(compound,Molecular,method)%>%
    summarize(meanCor=mean(corVal,na.rm=T))

  pred.lists<-do.call(rbind,apply(all.preds,1,function(x){
    res<-getFeaturesFromStringdf(x[['genes']],x[['Molecular']])
    print(as.data.frame(t(x)))
    res%>%left_join(as.data.frame(t(x)),by='Molecular')
  }))%>%
    select(-genes)%>%
    left_join(eval.sum)%>%
    arrange(desc(meanCor))
  
  pred.lists$numFeatures<-as.character(pred.lists$numFeatures)
    pred.lists$numSamples<-as.character(pred.lists$numSamples)

  write.csv(pred.lists,file='fullDataModelFeaturesAndPerf.csv')
  ##nanually upload for now
 ## synTableStore(pred.lists,'Regression models from all pilot data',parentId = 'syn22128879')
  
  DT::datatable(pred.lists)
  
  new.results<-all.preds%>% left_join(eval.sum)%>%
    arrange(desc(meanCor))%>%
    subset(numFeatures>2)%>%#subset(MSE<1500)%>%  
    mutate(doEnrich=TRUE)%>%
        subset(compound%in%c('Trametinib (GSK1120212)','Quizartinib (AC220)'))%>%
    subset(meanCor>0.1)%>%
    dplyr::select(var='compound',method,data='Molecular',genelist='genes',doEnrich)%>%
    rowwise()%>%
    mutate(enrich=paste(selectDataMatAndPlot(var,method,data,genelist,doEnrich)$Description,collapse=','))
  
  write.csv(new.results,'selectDRugsGOenrichment.csv')
  
```

### Network analysis

Next we take the top-performing signatures for the two drugs of interest (trametinib and quizartinib) and plot them using the PCSF. For now let's focus on the multi-omic predictors.

```{r plot graphs}
plotGraphOnData<-function(df,fname){
  print(fname)
  dtypes<-df$DataType
  
  genelist<-lapply(dtypes,function(x)
    unlist(strsplit(subset(df,DataType==x)$genelists,';')))
  
  allgenes<-unlist(genelist)
  
  names(genelist)<-dtypes

  ##remove phosphosties from original analysis  
  phospho=c()
  if('Phosphosite'%in%dtypes){
    phospho<-genelist$Phosphosite
  
        ##now we need to fix the gene list, since it's not going to match    
    phgenes<-data.frame(genes=phospho)%>%
      separate(genes, into=c('gene','mod'),sep='-')%>%
      mutate(modlist=strsplit(mod,split='s|t|y'))%>%
      apply(1,function(x) paste(x$gene,x$modlist,sep='-'))%>%
      unlist()%>%unique()
  
    phospho<-phgenes
  }
  prots=c()
  if('proteinLevels'%in%dtypes)
    prots<-genelist$proteinLevels
  
  genes=c()
  if("binaryMutations"%in%dtypes)
    genes<-genelist$binaryMutations
  
  prot.vals<-rep(1,length(prots))
  names(prot.vals)<-prots
  
  phos.vals<-rep(1,length(phospho))
  names(phos.vals)<-phospho
  
  gene.vals<-rep(1,length(genes))
  names(gene.vals)<-genes
  
  het=computePhosphoNetwork(phos.vals,prot.vals,gene.vals,nrand=100,beta=2,fname=fname)
  
  #library(PCSF)
  #plot.PCSF(het)
  return(het)
}


  plot.results<-pred.lists%>%
    subset(compound%in%c('Trametinib (GSK1120212)','Quizartinib (AC220)'))%>%
    subset(meanCor>0.1)%>%
    subset(Molecular!='mRNALevels')%>%
    #subset(Molecular=='Phosphosite')%>%
    rowwise()%>%
        mutate(fname=paste(c(method,compound,Molecular),collapse='_'))%>%
  group_by(fname)%>%
  nest(df=c(DataType,genelists))%>%
    select(df,fname)%>%
    purrr::pmap_dfr(.,.f=plotGraphOnData)

DT::datatable(plot.results)

##now get summary stats as well

```


Now we can explore specific gene signatures based on their performance and gene sets of interest.








